An empirical study of fixation for strategies in the Iterated Prisoner's Dilemma

### 2017-05-04 main.tex
Add literature.
An introduction to the PD.
Two sentences about emergence of cooperation study
and two sentences about the ZD.

@@

The Moran process was initially introduced in \cite{Moran1957} in a genetic
setting. It has since been used in a variety of settings including the
understanding of the spread of cooperative behaviour. However, as stated before,
these mainly consider non sophisticated strategies. Some work has looked at
evolutionary stability of strategies within the Prisoner's Dilemma \cite{Li2014}
but this is not done in the more widely used setting of the Moran process but in
terms of infinite population stability. In \cite{Baek2016} Moran processes are
looked at in a theoretic framework for a small subset of strategies. In
\cite{Lee2015} machine learning techniques are used to train a strategy capable
of resisting invasion and also invade any memory one strategy. Recent work
\cite{Hilbe2017} has investigated the effect of memory length on strategy
performance and the emergence of cooperation but this is not done in Moran
process context and only considers specific cases of memory 2 strategies.
% TODO Add discussion about ZD strategies and discuss how this corresponds to
% case of N = 2. Include pointing at \cite{Adami2013} which discusses how ZD
% strategies are not fantastic in population dynamics.
% Add \cite{Li2014}

@@

As described in \cite{Nowak} Consider the payoff matrix:

@@

Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
stochastic strategies. These are no longer a good match which highlights the
weakness of the analytical formulae that relies on the average payoffs. A
detailed analysis of the 164 strategies considered, using direct Moran processes
will be shown in the next Section.

>>>>

The Prisoner's Dilemma (PD)~\cite{Tucker1983} is a fundamental two person game 
in Game theory. Each player can choose between cooperation (C) or defection 
(D). The decisions are made simultaneously and independently. The payoffs of
the game are defined by the matrix $\begin{pmatrix} R & S \\ T & P
\end{pmatrix}$, where $T > R > P> S$ and $2R > T + S$. The PD is a one 
round game, but is commonly studied in a manner where the prior outcomes 
matter, the game then extends to its ’iterated’ form, the Iterated Prisoner's 
Dilemma (IPD).

@@

The Moran process was initially introduced in \cite{Moran1957} in a genetic
setting. It has since been used in a variety of settings including the
understanding of the spread of cooperative behaviour. For instance, cancer 
cells \cite{West2016}. Emergence of cooperative behaviour, also includes 
studies in spatial topologies \cite{Nowak2017}. However, as stated before, 
these mainly consider non sophisticated strategies. Some work has looked at
evolutionary stability of strategies within the Prisoner's Dilemma \cite{Li2014}
but this is not done in the more widely used setting of the Moran process but in
terms of infinite population stability. In \cite{Baek2016} Moran processes are
looked at in a theoretic framework for a small subset of strategies. 
The subset included memory one strategies, strategies that recall the events 
of the previous round only. In \cite{Press2012}, a set of memory one 
strategies, the zero determinant strategies, have been introduced. The ZD\@,
strategies are highly praised and in \cite{Stewart26062012} argued that 
generous ZD strategies are robust against invading strategies. However,
in \cite{Lee2015} machine learning techniques are used to train a strategy 
capable of resisting invasion and also able to invade any memory one strategy. 
Recent work \cite{Hilbe2017} has investigated the effect of memory length on 
strategy performance and the emergence of cooperation but this is not done in 
Moran process context and only considers specific cases of memory 2 strategies.
% TODO Add discussion about ZD strategies and discuss how this corresponds to
% case of N = 2. Include pointing at \cite{Adami2013} which discusses how ZD
% strategies are not fantastic in population dynamics.
% Add \cite{Li2014}

@@

As described in \cite{Nowak} consider the payoff matrix:

@@

Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
stochastic strategies. These are no longer a good match which highlights the
weakness of the analytical formula that relies on the average payoffs. A
detailed analysis of the 164 strategies considered, using direct Moran processes
will be shown in the next Section.
